\documentclass{article}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{soul}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage[]{fancyhdr}
\usepackage[margin=1in]{geometry}

\title{Protocol and tasks - MUPPETS viability}
\newcounter{comments}
\newcommand{\amogh}[1]{{\addtocounter{comments}{1}}{\color{red}{[\textbf{TODO Amogh \thecomments :}\ #1}]}}
\newcommand{\bradley}[1]{{\addtocounter{comments}{1}}{\color{violet}{[\textbf{TODO Bradley \thecomments :}\ #1]}}}
\newcommand{\zeina}[1]{{\addtocounter{comments}{1}}{\color{blue}{[\textbf{TODO Zeina \thecomments :}\ #1]}}}
\newcommand{\colin}[1]{{\addtocounter{comments}{1}}{\color{cyan}{[\textbf{TODO Colin \thecomments :}\ #1]}}}
\date{\today}


\begin{document}
\pagestyle{fancy}
\fancyfoot{}
\fancyhead{}
\fancyfoot[LO,RE]{\thepage \quad   LAST UPDATED \today}

\maketitle
\tableofcontents


\section{Task List}


\amogh{Make high throughput viral serial dilution script}

\amogh{Make flexible script to reorganize samples after sample identification?}

\bradley{Flesh out the day-by-day courses with Amogh}

\colin{Add in the protocol for difficult fungal handling}

\amogh{Fill out protocols}

\newpage

\section{Foreword}
We are receiving 60 distinct samples, with 2 replicates from NIST. These samples are 10 mL blood which are potentially frozen, and potentially not frozen. Each sample has between 0 and 3 organisms, which are a combination of fungi, viruses, and bacteria. We need to store the sample in 2 CONOPS (doubling treatment plates). The Cell Viability Core (CVC) are potentially unblinded to the samples. The treatment teams (Silver \& Marelli) are blinded to the samples to avoid preferential treatment. We need to report for each sample what was in it, how much, and how much survived after 7 days.

All samples need to be treated as BSL2+. All well plates need to have lids at all times. All handling of samples need to be done in the Tecan (sealed) or in a bio-safety cabinet. All biosafety bags which handle BSL2+ samples need to be sprayed down before placing in normal biosafety containers, including that from the Tecan. \amogh{I was forgetting some of the common sense safety stuff you probably know when converting from BSC best practices to Tecan best practices, perhaps it would be good to write them down}

\section{Protocols}
\begin{itemize}
    \item Media prep (\Cref{sec:media-prep})
    \item Cell culture calculations
    \item Tecan startup (\Cref{sec:tecan-start})
    \item Tecan shutdown (\Cref{sec:tecan-shut})
    \item Protocol - Bacterial, fungal serial dilutions (\Cref{sec:serial-dil-bacterial})
    \item Protocol - Viral serial dilutions (\Cref{sec:serial-dil-viral})
    \item Protocol - Sample identification with qPCR  (\Cref{sec:sample-ident})
    \item Protocol - qPCR setup for bacteria/fungi 
    \item Protocol - qPCR setup for virus 
    \item Protocol - OD reads (Method: \texttt{384 well plates read})
    \item Treatment Preparation and Conditions \bradley{}
    \item Handling of samples with hyphal fungi \colin{} 
    \begin{itemize}
        \item receive 60 samples (4 ml of blood in ORIGINAL 10 ML TUBES) handed to him by Amogh/Bradley
        \item Vortex ORIGINAL tubes, 1-2 at a time, for 4 rounds, 34 seconds each. (The breaks in between rounds are for Colin's poor fingers to rest). \textbf{[10 mins]}
        \item Transfer vortexed tubes to 5 tube racks (12 tubes per rack).
        \item Place first rack in bath sonicator. Make sure water is up to "fill" level.
        \item Turn on bath sonicator for 10 minutes. 
        \begin{itemize}
            \item 
        \end{itemize}
        \item Repeat for all 5 racks. \textbf{[1 h 15 mins]}
        \begin{itemize}
            \item Look for breakage of fungus ball clumps. If you're not seeing anything, possibly repeat certain samples.
        \end{itemize}
        \item Grab pre-prepared \zeina{plan to hand colin these labeled tubes} 5 ml tubes, clean, labeled 1-60, and put 100 um cell strainer on top
        \begin{itemize}
            \item  (make sure the width of the cell strainer is compatible with the 5 ml tubes not the 50 mls!!)
        \end{itemize}
    \item Pour or use serological pipette \colin{decide which one} to filter the 60 sonicated samples into the clean 5 ml labeled tubes. 
    \item For any remaining very large fungal balls stuck in filter, we would like to save them just in case. That way we are able to qPCR to identify the strain. \zeina{prepare a rack of 50 ml conicals on standby (ulabeled) just in case}
    \item \amogh{do we now need to give you a plate of fungus so it can be TECAN ready? + how do we transfer them? + can we make a plate map for this?}
    \end{itemize}
\end{itemize}

\subsection{Media prep}
\label{sec:media-prep}
\begin{description}
\item[Universal bacterial media (UBM)] TSB+BHI supplemented with NAD and Hemin. TSB - Mix 30g TSB powder into 1L media, autoclave. BHI - mix 37g BHI powder into 1L media, autoclave. 2000X Hemin and NAD stocks are stored in the -80 in GOLD513.
\item[Fungal media] Potato Dextrose Broth.
\item[Cell culture media for Vero cells] EMEM + 10\% FBS. We use 200uL per well, each 96 well plate needs 20mL of cells resuspended in media.
\end{description}

\subsection{Cell culture calculations}
\label{sec:cell-culture}
\begin{table}[h]
  \centering
\begin{tabular}{c|c}
Seeding density & 4e4 \\
Wells per plate & 100 \\
Replicates & 4 \\
CONOPS & 2 \\
Number of treatments & 4\\
Number of dilutions & 6\\
Total plates required &  192\\
\end{tabular}

\end{table}

\subsection{Tecan startup}
\label{sec:tecan-start}
\begin{enumerate}
\item Turn Tecan power on. The power switch is located on the white box next to the computer below the deck.
\item Start FluentControl, the Tecan software. This can take 3-5 minutes. Acknowledge the warning that the software is not meant of clinical use.
\item Ensure the deck is cleared of any old tip boxes, tip box lids, plates, stray pipette tips etc.
\item Initialize the instrument. On the menu bar on top, Click Run > Initialize instrument.
\item Examine the RGA, the robotic arm fingers
  \begin{enumerate}
  \item Pull down the RGA until it is flat against one of the plate nests. Ensure the fingers are both horizontal. If not, align the fingers.
  \item Firmly but slowly move the fingers up and down to ensure the screw is tight. If the finger is pivoting in the z-direction, tighten the screw at the base of the finger using the TORX15 or TORX20 screw driver.
  \item Spray deck with 70\% ethanol, wipe down.
  \item Place bioharzard bag in the waste chute.
  \end{enumerate}
\end{enumerate}


\subsection{Tecan shutdown}
\label{sec:tecan-shut}
\begin{enumerate}
\item Take the biohazard bag out of the trash chute carefully.
\item Clear any remaining labware.
\item Spray down with 70\% ethanol. Let sit for 5 minutes, wipe down thoroughly.
\item CLose the FluentControl software.
\item Power off the Tecan using the switch on the white controller box placed below the deck.
\end{enumerate}

\subsection{Bacterial/Fungal Serial dilutions}
\label{sec:serial-dil-bacterial}
NIST samples are expected to have 1e6 cells/mL. We are assaying viability of ~10$\mu$L of sample, or about 1e4 cells. We will perform 6 serial dilutions per treatment.

\begin{itemize}
\item Pre-fill 384 well clear plates with UBM (\Cref{sec:media-prep}) for each day.
\item  Load serial dilution plates into the Cytomat. 
\item Fill a 100mL trough with \bradley{final decision on Monday}.
\item Follow further instructions  provided by method: \texttt{Serial Dilutions - Bacterial/Fungal}).
\end{itemize}

\subsection{Viral dilutions}
We will need 4 seeded plates per dilution. If unblinded, we will need 24 seeded 96 well plates for 6 dilutions.
\label{sec:serial-dil-viral}
\begin{itemize}
\item Follow instructions on method: \texttt{Serial Dilutions - Viral})
\end{itemize}

\subsection{Sample identification with qPCR }
\label{sec:sample-ident}
\textit{A priori} the sample composition is unknown, but we have designed probes for the 41 species that we expect to comprise the samples.

On Day 0 we will assay all 60 samples with all probes. 
\begin{itemize}
\item Stamp out qPCR plates with two consecutive rows of MM filled with 41 probes. (See \Cref{tab:probe-layout})
\item Assay 8 samples at a time, distributed across all columns. 
  \begin{itemize}
  \item Transfer the first column of the sample plate into a 96 well plate across columns.
  \item Use 4 tip boxes to stamp out samples into qPCR plate.
  \end{itemize}
\item This will require 9 qPCR plates. Make all mastermixes with RT.
\end{itemize}

\begin{table}
  \centering
{\tiny
\begin{tabular}{lrrrrrrrrrrrrrrrrrrrrrrrr}
 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 & 21 & 22 & 23 & 24\\
\hline
A & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 & 21 & 22 & 23 & 24\\
B & 25 & 26 & 27 & 28 & 29 & 30 & 31 & 32 & 33 & 34 & 35 & 36 & 37 & 38 & 39 & 40 & 41 &  &  &  &  &  &  & \\
C & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 & 21 & 22 & 23 & 24\\
D & 25 & 26 & 27 & 28 & 29 & 30 & 31 & 32 & 33 & 34 & 35 & 36 & 37 & 38 & 39 & 40 & 41 &  &  &  &  &  &  & \\
E & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 & 21 & 22 & 23 & 24\\
F & 25 & 26 & 27 & 28 & 29 & 30 & 31 & 32 & 33 & 34 & 35 & 36 & 37 & 38 & 39 & 40 & 41 &  &  &  &  &  &  & \\
G & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 & 21 & 22 & 23 & 24\\
H & 25 & 26 & 27 & 28 & 29 & 30 & 31 & 32 & 33 & 34 & 35 & 36 & 37 & 38 & 39 & 40 & 41 &  &  &  &  &  &  & \\
I & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 & 21 & 22 & 23 & 24\\
J & 25 & 26 & 27 & 28 & 29 & 30 & 31 & 32 & 33 & 34 & 35 & 36 & 37 & 38 & 39 & 40 & 41 &  &  &  &  &  &  & \\
K & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 & 21 & 22 & 23 & 24\\
L & 25 & 26 & 27 & 28 & 29 & 30 & 31 & 32 & 33 & 34 & 35 & 36 & 37 & 38 & 39 & 40 & 41 &  &  &  &  &  &  & \\
M & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 & 21 & 22 & 23 & 24\\
N & 25 & 26 & 27 & 28 & 29 & 30 & 31 & 32 & 33 & 34 & 35 & 36 & 37 & 38 & 39 & 40 & 41 &  &  &  &  &  &  & \\
O & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 & 21 & 22 & 23 & 24\\
P & 25 & 26 & 27 & 28 & 29 & 30 & 31 & 32 & 33 & 34 & 35 & 36 & 37 & 38 & 39 & 40 & 41 &  &  &  &  &  &  & \\
\end{tabular}
}
  \caption{Probe layout for Day 0 sample identification.}
  \label{tab:probe-layout}
\end{table}

\section{Treatments} \label{treatments}
A total of 10 treatments will be prepared and applied to all 60 samples on  \ref{day0instructions}, the treatment conditions have been decided as follows. The following calculations assume we are doing 2 treatment replicates that go into dilutions. We expect 1e6 cells/mL or 1e4 cells/well. We will perform 6x 10-fold serial dilutions to account for carryover. See \ref{tab:dilution-plan-day-0} for a reference of the treatments and how many plates, and dilution plates are required. For the preparation of solutions, double the treatment per each organism type, and each treatment type. For treatment plates, each plate will have 36 microliters of treatment, to which 14 microliters of sample will be placed, or a 1/3 dilution. This has been verified for blood work.

\begin{table} 
  \centering
  \begin{tabular}[]{c|c|c|c}
    \textbf{Organism} & \textbf{Treatments} & \textbf{Treatment} & \textbf{Total plates required} \\
     &  & \textbf{count} & \textbf{(2 CONOPS)} \\
    \hline
    \textit{Bacteria} & Sample  & & \\
    \hline
    & & 1 & 16\\
    \hline
    \textit{Virus} & Sample  & & \\
    \hline
    & & 1 & 16\\
    \hline
    \textit{Fungi} & Sample  & & \\
    \hline
    & & 1 & 16\\
    \hline

  \end{tabular}
  \caption{Summary of dilution plates required for the Day 0 IV\&V run.}
  \label{tab:dilution-plan-day-0}
\end{table}


\begin{table}
  \centering
  \begin{tabular}[]{c|c|c|c|c}
    \textbf{Organism} & \textbf{Treatments}  & \textbf{Treatment} & \textbf{Total plates required} & \textbf{Plate ID}\\
     &   & \textbf{count} & \textbf{(2 CONOPS)} & \\
    \hline
    \textit{Bacteria} & PODS 1.5w   & & & 1\\
     & PODS 1.6w   & & & 2\\
     & pullulan & & & 3\\
     & dry blood   & & & 4\\
     & wet blood   & & & 5\\
    \hline
    &  & 5& 60& \\
    \hline
    \textit{Virus} & PODS 1.5w & & & 6\\
     & PODS 1.5WV & & & 7\\
     & dry blood   & & & 8\\
     & wet blood   & & & 9\\
             & 1:10 wet blood:VTM   & & & 10\\
 & pullulan & & & 11\\
    \hline
    &  & 6& 60 & \\
    \hline
    \textit{Fungi} & PODS 1.5 & & & 12\\
     & PODS 1.6 & & & 13\\
     & dry blood   & & & 14\\
     & wet blood   & & & 15\\
    \hline
    &  & 4 & 48 & \\
    \hline

  \end{tabular}
  \caption{Summary of dilution plates required for the Day 7 IV\&V run.}
  \label{tab:dilution-plan-day-7}
\end{table}

\newpage
\section{Preparation for Day 0}\label{sec:day0-prep}
\subsection{Lab Changes}
\begin{enumerate}
    \item \amogh{\st{Moving the centrifuge} Waiting on Sam}
    \item \bradley{We need to open 6 full boxes of tips of both sizes}
    \item \zeina{Storage/workplace re-organization}
    \begin{enumerate}
        \item Clear/prepare the plate-filling area, store 384 well plates next to it
        \item Clear and tape off areas for 384 well plate storage after incubation
        \item Clear and tape off the vacuum filtration/treatment preparation area \bradley{I think we should just leave the pipettes i use to do this stuff next to the vacuum filtration/media zone, makes sense that they are there, but also need to clean out the impromptu storage}
    \end{enumerate}
    \item \colin{the declaration and preparation of a fungal zone with the coming sonication bath, a vortex mixer, place to set samples}
\end{enumerate}

\subsection{Labeling System/Plate Maps}
\label{sec:labeling}

The IV\&V experiment ID is \textsc{MP52}.
\subsubsection{Sample handling}
Template: \textsc{MP52}-\texttt{S<SAMPLE ID>}. See \Cref{tab:sample-map} for layout.

\begin{table}
\centering
\begin{tabular}{l|rrrrrrrrrrrr}
 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12\\
\hline
A & 1 & 9 & 17 & 25 & 33 & 41 & 49 & 57 &  &  &  & \\
B & 2 & 10 & 18 & 26 & 34 & 42 & 50 & 58 &  &  &  & \\
C & 3 & 11 & 19 & 27 & 35 & 43 & 51 & 59 &  &  &  & \\
D & 4 & 12 & 20 & 28 & 36 & 44 & 52 & 60 &  &  &  & \\
E & 5 & 13 & 21 & 29 & 37 & 45 & 53 &  &  &  &  & \\
F & 6 & 14 & 22 & 30 & 38 & 46 & 54 &  &  &  &  & \\
G & 7 & 15 & 23 & 31 & 39 & 47 & 55 &  &  &  &  & \\
H & 8 & 16 & 24 & 32 & 40 & 48 & 56 &  &  &  &  & \\
\end{tabular}
\caption{Sample ID map.}
\label{tab:sample-map}
\end{table}

\subsubsection{Treatment labeling}
Template: \textsc{MP52}-\texttt{<PLATEID>}. See \Cref{tab:dilution-plan-day-7} for metadata.

\subsubsection{Dilution labeling}

Template: \textsc{MP52}-\texttt{<PLATEID>}-\texttt{<DILUTIONID>}. 
We will perform 6 dilutions per sample.

\subsection{Media, plate, and sample preparation}
\textbf{Bacterial media} We need 16 384 well plates filled with 55uL of UBM/well, i.e. 400mL of UBM. Plates need to be labeled and filled by 2025-05-04. 

\textbf{Fungal media} We need 16 384 well plates filled with 55uL of UBM/well, i.e. 400mL of Yeast media (PDB). Plates need to be labeled and filled by 2025-05-04.

\textbf{Seeded Vero plates} We need 16 96 well plates seeded with 200uL of 10\% confluent Vero cells. Plates need to be labeled and filled by 2025-05-04.

\textbf{Drying Caps} We need 30 of the milled drying caps filled with fresh 3a zeolite, and capped with aeraseals, placed into a drying container. 

\textbf{Drying containers} We need all drying containers filled with zeolite, dryrite (if used) 

\textbf{Tubes for Dividing Samples Upon Receipt} We need to pre-label and designate the tubes into three sets: Amogh, C

\section{Preparation for Day 7 and 8}\label{sec:day7-prep}
\textbf{Bacterial media} We need 60 384 well plates filled with 55uL of UBM/well, i.e. 1.5L of UBM. Plates need to be labeled and filled by 2025-05-09.

\textbf{Fungal media} We need 48 384 well plates filled with 55uL of UBM/well, i.e. 1.1L of Yeast media (PDB). Plates need to be labeled and filled by 2025-05-09.

\textbf{Seeded Vero plates} We need 60 96 well plates seeded with 200uL of 10\% confluent Vero cells. Plates need to be labeled and seeded by 2025-05-09 at most. 

\section{Day 0 Order of Operations} \label{day0instructions}

\begin{enumerate}
    \item GOTO Tecan, and run the startup verification script to make sure that it is lifting plates, grabbing pipettes tips, and that the cytomat is working. \amogh{}
    \item Check if samples (60x10mLx2 replicates) are actually frozen.
    \item \st{If frozen $\rightarrow$ add half to freezer} Move sample duplicates to freezer to verify by qPCR.
    \item \amogh{This is a precaution against fungi clogging the FCA tips } Spin down tubes briefly.
    \item Convert sample tubes to 1mL 96 well plate format for tecan + divide into 3 plates\amogh{Make Tecan script after optimizing for sample type} \zeina{account for these plates in plate maps}
    
    \begin{enumerate}
        \item Pipette 1 ml of each sample tube into deep well plates (Xx 96 deep wells, ~1 ml? each) \amogh{check desired amount, how many deep wells?} 
        \item Pipette 4 ml of each sample tube into deep well plates for the Paulsson team \amogh{check desired amount}
        \item Pipette a small amount of the sample onto a plate for microscopy (2x 48 wells, or 1x 96well, ~100uL each) 
        \item \bradley{} will observe samples for large fungus clotting, etc.
        \begin{enumerate}
            \item If fungus comes dispersed, maybe handle on robot already 
            \item If large fungal particles are observed, hand\textbf{ THE REMAINING SAMPLE IN ITS ORIGINAL TUBES} to the Colin \colin{}, and he can handle them with sonication and mixing (per his protocol \amogh{how do i reference the protocols section? -z}) before handing back to Tecan
        \end{enumerate}
    \end{enumerate}
    \item At this point, the samples need to be handled on the robot for the following 3 tasks in order:
    \begin{enumerate}
        \item Day 0 identification (what is in each sample, if Cell Viability Core remains blinded)
        \item dilution into treatment plates, and set up to dry
        \item Day 0 viability (how many are in each sample) 
    \end{enumerate}
    
    \item All 60 samples will be treated separately according to \ref{treatments}, summarized below:
    
    \begin{enumerate}
        \item 4 treatments which will be handed as “bacterial” samples
    \end{enumerate}
    \begin{enumerate}
        \item 3 treatments which will be handled as “viral” samples
    \end{enumerate}
    \begin{enumerate}
        \item 3 treatments which will be handled as “fungal” samples
    \end{enumerate}
\end{enumerate}

\section*{Day 1 Order of Operations} \label{day1instructions}
\begin{enumerate}
    \item On Tecan: run the startup verification script to make sure that it is lifting plates, grabbing pipettes tips, and that the cytomat is working. \amogh{}
    \item Take out the incubating plates from day 0 viability to the benchtop to prevent evaporation
    \item Prepare the dilution plates for day 1 viability of all treatment plates
\end{enumerate}

\section*{Day 2 Order of Operations} \label{day1instructions}
\begin{enumerate}
    \item Take out the incubating plates from day 1 viability to the benchtop to prevent evaporation
    \item Do the qPCR viability protocol for bacteria \textbf{day 0} plates to measure viability (round \textbf{1})
    \item Do the qPCR viability protocol for fungal \textbf{day 0} plates to measure viability (round \textbf{1})
\end{enumerate}

\section*{Day 3 Order of Operations} \label{day1instructions}
\begin{enumerate}
    \item Do the qPCR viability protocol for bacteria \textbf{day 0} plates to measure viability (round \textbf{2})
    \item Do the qPCR viability protocol for fungal \textbf{day 0} plates to measure viability (round \textbf{2})
\end{enumerate}

\section*{Day 7 Order of Operations} \label{day7instructions}
\begin{enumerate}
    \item GOTO Tecan, and run the startup verification script to make sure that it is lifting plates, grabbing pipettes tips, and that the cytomat is working. \amogh{}
    \item Prepare the dilution plates for viability for the frozen samples
\end{enumerate}

\section*{Day 8 Order of Operations} \label{day8instructions}
\begin{enumerate}
    \item GOTO Tecan, and run the startup verification script to make sure that it is lifting plates, grabbing pipettes tips, and that the cytomat is working. \amogh{}
    \item Take out the incubating plates from day 7 viability to the benchtop to prevent evaporation
    \item Prepare the dilution plates for viability for the frozen samples
\end{enumerate}

\section*{Day 9 Order of Operations} \label{day8instructions}
\begin{enumerate}
    \item GOTO Tecan, and run the startup verification script to make sure that it is lifting plates, grabbing pipettes tips, and that the cytomat is working. \amogh{}
    \item Take out the incubating plates from day 8 viability to the benchtop to prevent evaporation
    \item Do the qPCR viability protocol for bacteria \textbf{day 7 RT} plates to measure viability (round \textbf{1})
    \item Do the qPCR viability protocol for fungal \textbf{day 7 RT} plates to measure viability (round \textbf{1})
\end{enumerate}

\section*{Day 10 Order of Operations} \label{day8instructions}
\begin{enumerate}
    \item GOTO Tecan, and run the startup verification script to make sure that it is lifting plates, grabbing pipettes tips, and that the cytomat is working. \amogh{}
    \item Do the qPCR viability protocol for bacteria \textbf{day 7 frozen} plates to measure viability (round \textbf{2})
    \item Do the qPCR viability protocol for fungal \textbf{day 7 frozen} plates to measure viability (round \textbf{2})
\end{enumerate}


\section*{Appendix - Plate Maps} \label{platemaps}



\end{document}

%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: t
%%% End:
